Embedding Dimension of Polyhedral Losses

### 2020-01-29 colt-20/embed-dim.tex
conditions for 1d
was probably fixing some typos

\cite{ramaswamy2018consistent} study the abstain property in great length, presenting a $\ceil \log_2(n)$ dimension embedding of the abstain property.
However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give anything tighter than the trivial $1 \leq \elicembed(\abstain{\alpha})$ for $\alpha \leq 1/2$.

>>>>

\cite{ramaswamy2018consistent} study the abstain property in great length, presenting a $\ceil {\log_2(n)}$ dimension embedding of the abstain property.
However, it is unclear if this bound is tight, as the previously studied lower bounds of~\cite{ramaswamy2016convex} do not work well for this property, failing to give anything tighter than the trivial $1 \leq \elicembed(\abstain{\alpha})$ for $\alpha \leq 1/2$.
